### 2021-04-09 Chapter-6/Chapter-6.tex
Updates from Overleaf

\textbf{Kernel Space Side-channel Vulnerability Detection.}

\textbf{Compiler-assisted Side-channel Vulnerability Analysis And Mitigation.}

\textbf{Static Side-channel Quantification.}

>>>>

\textbf{Kernel Space Side-channel Vulnerability Detection.} There are several side-channel vulnerability detection tools together with the dissertation tool. Most of the tools are designed to analyze the side-channel leakages in user-level applications like cryptographic libraries. It is reasonable since many side-channel attacks are used to break cryptographic applications. Recently, researchers also started to focus on side-channel attacks~\cite{cao2016off} inside the kernel space. However, it is non-trivial to apply existing side-channel detection tools in the Linux kernel. Take the method in the dissertation, for example. We may have the following challenges. First, our proposed tools in the dissertation rely on the dynamic binary instrumentation frameworks to collect the runtime information. As for kernel programs, a similar task can be achieved by some whole system emulators like BitBlaze~\cite{song2008bitblaze} and S2E~\cite{chipounov2012s2e}. S2E uses a modified Linux kernel and QEMU to trace the kernel components. S2E uses QEMU 1.0, which does not support the latest Linux kernel. The engineering efforts of extending S2E to work on the latest kernel are significant. Second, the kernel has very complicated control-flow graphs compared to cryptography libraries. Some vulnerabilities need to be triggered by specific input from the user space applications or devices. Our tool can not handle interruptions and exceptions. But they are common inside the kernel. On the positive side, we expect there are plenty of leakage sites inside the kernel. The dissertation provide the approaches to pick up ``severe'' leakages automatically.

\textbf{Compiler-assisted Side-channel Vulnerability Analysis and Mitigation.}
We propose to mitigate the side-channel leakages in a compiler backend. For example, the conditional execution can be eliminated by using the masks. Eliminating side-channel leakages from compilers is not a brand new idea. Coppens et al.~\cite{Coppens:2009:PMT:1607723.1608124} propose several methods to remove several approaches to eliminate all potential leakages that are related to data flow and control flow.  GNU toolchain adds new options (\textsf{-mlfence-after-load}, \textsf{-mlfence-before-indirect-branch}) to mitigate the Load Value Injection (LVI) attack during the compilation. Coppens et al.'s approach has a slowdown with a factor from 2 to 24. The LVI harden binaries generated from GNU toolchains takes 6-10x longer to run. The performance impact from the aggressive mitigation. For example, GNU toolchains inset LFENCE before any possible vulnerable instructions, which include all load instructions, all indirect branches, and return instructions. We plan only to change those points that are more likely to leak sensitive information. Even more, with the tool presented in the dissertation, we can only modify part of the ''severe`` leakage sites.
